Magnitude of simple rules in investment strategies of algorithmic trading

### 2013-06-04 Article/Article20130603/tewi-paper-template.tex
Conclusion

\section{Conclusions}
Ut purus. Nullam facilisis porttitor enim. Vestibulum nulla massa, ultricies
sed, molestie luctus, imperdiet eget, mi. \\
\indent Integer commodo ipsum vitae enim. Morbi mollis nunc suscipit nisl.
Class aptent taciti sociosqu ad litora torquent per conubia nostra, per
inceptos himenaeos. Nam urna lacus, placerat posuere, dapibus eget, gravida
at, lorem. Aliquam nec justo eu dui semper fringilla. Aliquam vitae urna.
Morbi mattis consectetur ante. Ut ante massa, vestibulum ut, accumsan ac,
convallis quis, orci. Pellentesque at ipsum vitae quam laoreet tristique. Cras
vel nunc. Nulla facilisi.\\
\indent Pellentesque fringilla nulla vitae metus varius faucibus. Fusce aliquet
vehicula risus. Donec pulvinar viverra lectus. Nam tristique. Nulla malesuada
metus nec purus. Ut aliquam diam. Phasellus eu dui vel ipsum aliquet
vestibulum. Quisque ullamcorper, ligula in placerat imperdiet, risus risus
malesuada dolor, ut scelerisque ipsum nisi eu urna. Mauris bibendum tortor
condimentum mauris.

>>>>

\section{Conclusions}
\indent Suggested simple strategy is suitable only for algorithmic trading, even in absolute simplest form it seems to be interesting. As it’s been written in the introduction, more from cognitive point of view, than for the transaction value.\\
\indent This strategy can be modified in many ways.  Eg. in case of suggestions of simultaneous opening long and short positions better is to abandon work than opening both positions (due to transaction costs). The opening of another position in the same direction, eg. long position after closing the previous long position is senseless, it’s better to continue already opened position. These are two simplest ways to improve strategy. There are probably many ways to filter openings that allow to preserve only the most valuable due to profit events. Purpose of this paper was to prove the thesis, that even the simplest strategy has some potential profit, whose using is fascinating challenge.\\
\indent The authors believe, due to observing results of experiments, that the thesis of this dormant potential has been acknowledged.
